Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2024-01-13 manuscript/manuscript.Rmd
committing various changes

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Fig \ref{fig:agg-performance-all}A) and locations (\nameref{fig:performance-locations-rel}A Fig). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers. Overall, low variance in forecast performance was closely linked with good mean performance (Fig \ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers, as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

>>>>

For cases, crowd forecasts had a lower mean weighted interval score (WIS, lower values indicate better performance) than both the renewal model and the Hub ensemble across all forecast horizons (Fig \ref{fig:agg-performance-all}A) and locations (\nameref{fig:performance-locations-rel}A Fig). For two week ahead forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for crowd forecasts and 1.40 for the renewal model (\nameref{tab:score-table-2} Table). Across all forecasting approaches, locations and forecast horizons, the distribution of WIS values was very right-skewed, and average performance was heavily influenced by outliers (see Fig \ref{fig:distribution-scores}). Overall, low variance in forecast performance was closely linked with good mean performance (Fig \ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A), suggesting that the ability to avoid large errors was an important factor in determining overall performance. The impact of outlier values was especially pronounced for the renewal model, which had more outliers, as well as the highest standard deviation of WIS values (standard deviation of the WIS relative to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed more stable performance.

### 2024-01-13 manuscript/pcbi.1010405_PSEA.tex
committing various changes

For cases, crowd forecasts had a lower mean weighted interval score
(WIS, lower values indicate better performance) than both the renewal
model and the Hub ensemble across all forecast horizons (Fig
\ref{fig:agg-performance-all}A) and locations
(\nameref{fig:performance-locations-rel}A Fig). For two week ahead
forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for
crowd forecasts and 1.40 for the renewal model
(\nameref{tab:score-table-2} Table). Across all forecasting approaches,
locations and forecast horizons, the distribution of WIS values was very
right-skewed, and average performance was heavily influenced by outliers
(see Fig \ref{fig:distribution-scores}). Overall, low variance in
forecast performance was closely linked with good mean performance (Fig
\ref{fig:agg-performance-all}H and \ref{fig:agg-performance-all}A),
suggesting that the ability to avoid large errors was an important
factor in determining overall performance. The impact of outlier values
was especially pronounced for the renewal model, which had more
outliers, as well as the highest standard deviation of WIS values
(standard deviation of the WIS relative to the WIS sd of the Hub
ensemble was 1.54 at the two weeks ahead horizon), while the ensemble of
crowd forecasts (rel. WIS sd 0.76) and the Hub ensemble (= 1) showed
more stable performance.

@@

\section*{References}
\bibliographystyle{plos2015}
\bibliography{germanpolishpaper.bib, references.bib}

>>>>

For cases, crowd forecasts had a lower mean weighted interval score
(WIS, lower values indicate better performance) than both the renewal
model and the Hub ensemble across all forecast horizons (Fig
\ref{fig:agg-performance-all}A) and locations
(\nameref{fig:performance-locations-rel}A Fig). For two week ahead
forecasts, mean WIS relative to the Hub ensemble (= 1) was 0.89 for
crowd forecasts and 1.40 for the renewal model
(\nameref{tab:score-table-2} Table). Across all forecasting approaches,
locations and forecast horizons, the distribution of WIS values was very
right-skewed, and average performance was heavily influenced by
outliers. Overall, low variance in forecast performance was closely
linked with good mean performance (Fig \ref{fig:agg-performance-all}H
and \ref{fig:agg-performance-all}A), suggesting that the ability to
avoid large errors was an important factor in determining overall
performance. The impact of outlier values was especially pronounced for
the renewal model, which had more outliers, as well as the highest
standard deviation of WIS values (standard deviation of the WIS relative
to the WIS sd of the Hub ensemble was 1.54 at the two weeks ahead
horizon), while the ensemble of crowd forecasts (rel. WIS sd 0.76) and
the Hub ensemble (= 1) showed more stable performance.

@@

\section*{References}
